Supplementary material

### 2023-06-26 analyses/scripts/S4_Table.Rmd
Fixed some path issues

```{r}
here::i_am("analyses/scripts/full_data_extraction_citation_table.Rmd")
#I/O paths
figs_dir <- "analyses/figs"
data_dir <- "analyses/data"
scripts_dir <- "analyses/scripts"

@@

```{r load_data}
#' re-run the data cleaning step, in case something has changed 
#' TO DO: Use GNU make for this

source(here::here(scripts_dir, "orv_models_review_data_cleaning.R"))

# The data with citations 
compact_data_with_citation_keys <- read_rds(
  here::here(data_dir, 'compact_data_with_citation_keys_cleaned.rds'
  ))
```

>>>>

```{r}
# Paths
figs_dir <- "../figs/"
data_dir <- "../data"
scripts_dir <- "../scripts"

@@

```{r load_data}
.args <- c(here::here("data", "compact_data_with_citation_keys_cleaned.rds"))
# The data with citations 
compact_data_with_citation_keys <- readRDS(.args[1])
```
